### 2018-09-27 paper.tex
Wip

\subsection{Use a Published Model}

@@

In the case of a single developer who has no interest in publishing
models or otherwise supporting users, Guild AI model abstractions
provide value. By implementing models as units of operations, as is
the case with Guild AI model packaging, developers ensure their models
are easy to use from the early stages of development. This streamlines
the development process as developers can repeatedly run and iterate
through model operations using high level commands with well defined,
self documenting interfaces.

@@

@@

@@

@@

- What is a run (from an operation)

- What is a run concretely (i.e. directory, etc.)

@@

@@

@@

@@

\subsection{Archiving and Restoring Runs}

\subsection{Run Dependencies}

\subsection{Remote Runs}

@@

@@

- Core - written in Python, etc.

@@

@@

@@

@@

@@

@@

@@

\subsection{Remote Environments}

@@

- Apache 2.0

>>>>

\subsection{Use a Published Model}
\label{sec:use-model}

@@

In the case of a single developer who has no interest in publishing
models or otherwise supporting users, Guild AI model abstractions
provide value. By implementing models as units of operations, as is
the case with Guild AI model publishing, developers ensure their
models are easy to use from the early stages of development. This
streamlines the development process as developers can repeatedly run
and iterate through model operations using high level commands with
well defined, self documenting interfaces.

@@

The final use case discussed involves managing tracking run artifacts.
During both model development and use, it's useful to formally manage
the artifacts both generated and consumed by model operation. This is
similar to source code revision control, where developers can move
backward and forward in time to view their work. In the case of Guild
AI, the revisions are the results of data preparation, training
experiments, model optimizations---anything that might be generated by
an operation.

Section~\ref{sec:runs} provides more details about Guild AI run
management.

@@

Section~\ref{sec:use-model} describes the case of using published
models. This section provides more details on model usage in Guild AI.

@@

Packaged models are models that have been bundles with supporting code
and metadata into a Python wheel distribution. To generate a package,
a developer or packager must include a \verb|package| definition in
the project Guild file and then run the \verb|guild package| command.

Listing~\ref{lst:package} contains a sample \verb|package| definition.

\begin{lstlisting}[
    caption=Sample package definition,
    label={lst:package}]
package: sample-project
version: 1.0
description: Sample packaged project
url: https://my.co/packages/sample
author: John Doe
author-email: john@my.co
license: Apache 2.0
requires: [keras, Pillow, matlab]
\end{lstlisting}

Given a Guild file with such a package definition, Guild AI will
generate a Python wheel distribution that can be used to install any
models defined in the package.

@@

A \emph{run} is a formally managed file system artifact generated by
an operation. Runs may also refer to the operating system process
associated with a running operation.

Runs contain critical information for tracking and understanding what
happened during an operation:

\begin{itemize}
\item Run metadata such as the associated model and operation, status,
  start and stop times, operating system command and environment, and
  resolved dependencies
\item Output generated by the run---specifically the operating system
  process standard output and standard error
\item Files used by the operation (resolved resource sources)
\item Files generated by the operation
\end{itemize}

@@

Runs are started using the \verb|guild run| command and referencing a
model operation. Operations may be run with additional flag values
provided on the command line in the format \verb|NAME=VALUE|.

Here's an example of running an operation with flag values:

{\footnotesize
\begin{verbatim}
 $ guild run mnist:train \
     steps=10000 \
     batch-size=64 \
     learning-rate=0.0001
\end{verbatim}}

@@

Runs may be listed using the \verb|guild runs| command. Runs are
displayed with their unique ID, operation name, start time, status,
and user label.

Listed runs may be filtered by status, operation, and label.

@@

Information about one or more runs may be displayed using the
\verb|guild runs info| command. By default, high level run information
such as the run ID, operation, start time, command, exit status, and
operting system pid are displayed. Additional command options may be
used to view more run information including files, flag values,
dependencies, and operation output.

@@

One or more runs may be deleted using the \verb|guild runs rm|
command. Runs may be deleted using status, operation, or label.

Guild AI will restore deleted runs with \verb|guild runs restore| and
permanently delete runs using \verb|guild runs purge|.

@@

\subsection{Testing models}

@@

Guild AI is written in the Python programming language. It makes use
of a number of excellent open source libraries, many of which are
listed below.

@@

Guild AI is primarily a command line tool. Users type Guild AI
commands in the form:

{\footnotesize
\begin{verbatim}
guild COMMAND [ARG]...
\end{verbatim}}

Guild AI makes use of the Click Python library (ref) to implement its
core command line processingn support.

@@

Guild AI supports YAML (ref) as its configuration language for both
Guild files and user configuration. It uses the PyYAML Python library
(ref) for low level parsing.

Guild AI has implemented a novel scheme for configuration reuse, which
supports multiple inheritance, file includes, and section
includes. The reuse support allows Guild AI developers to maintain
complex model configurations with easily managed abstractions.

@@

Guild AI implements its own resource resolution scheme, which is used
to setup runs with required resource sources. Guild makes use of
directed acyclical graphs (DAGs) to model and efficiently resolve
complex interdependencies across operation.

@@

Guild AI supports model testing through a novel configuration scheme
that integrates with model definitions. Tests may be defined for one
or more models, each running and verifying one or more operations.

@@

Guild AI packages are valid Python wheel distributions. The underlying
libraries used to install Guild packages are the same as those used by
the \verb|pip| pgrogram to install PyPI packages. As a result, Guild
AI can be used to install PyPI packages and pip can be used to install
Guild AI packages---the process is the same in both cases.

@@

Guild AI uses a run indexing scheme to optimize run queries when
comparing runs and uses the Whoosh Python library (ref) in support
that.

@@

Guild AI provides various visualization tools, including its own run
viewer (Guild View) and integration with TensorBoard (ref).

Guild View is impemented using the VueJS library (ref) for the front
end and Werkzeug (ref) for the HTTP API back end.

@@

Guild AI is freely available under the Apach 2.0 open source
license. It has been under active development for the last two years
and undergone significant revision and updates during that time based
on user feedback and real world application development.
